Variable Selection in Convex Function Estimation

### 2013-10-04 tex/scam/appendix.tex
appendix update
proof and result update

Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]
It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.

@@

$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
\[
min_{f_k} \{ \E( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k))^2 \,:\, \E f_k(X_k) = 0 \}
\]
for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
\end{lemma}

@@

By the assumption that , we know that, for all $x_k$,
\begin{align*}
 \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
\end{align*}

@@

For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0 + w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0 + w} = \frac{1}{n} \sum_i f_0(X^{(i)}) + w_i $ and $\mu = \E f_0(X)$. Note that we \emph{subtract} out the mean in the two risk definitions.

@@

@@

\begin{lemma}
\label{lem:minus_one_risk_increase}
Suppose assumptions A1' and A4 hold.

@@

Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}^s[b,B,L], f_k \trm{ centered} \}$.

Suppose $n$ is large enough such that $c L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \right) \rightarrow 0$.

Then, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
\end{theorem}

@@

$f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered. Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$.

\begin{align*}
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq \| y - f^{*s} + \bar{f}^{*s} \|_n^2  - \| y - f^{*s}\|_n^2 \\
	&\leq 2\|y-f^{*s}\|_n \|\bar{f}^{*s}\|_n + \|\bar{f}^{*s}\|_n^2 
\end{align*}

Because each $f_k^{*s}$ is bounded by $B$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}_k^{*s}| \leq B\sqrt{\frac{1}{cn} \log n}$. By an union bound therefore, with probability at least $1-\frac{C}{n}$, $\|\bar{f}^{*s}\|_n \leq B\sqrt{\frac{1}{cn} \log sn}$.

\begin{align*}
\| y - f^{*s} \|_n &= \| f_0 + w - f^{*s} \|_n \\
	&\leq \| f_0 - f^{*s} \|_n + \|w\|_n \\
\end{align*}

@@

So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
\[
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
\]

Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.

@@

$\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $L$. By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.

$|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2L \lambda_n$.

$\tau'_n$, as shown above, is at most $2sB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.

For $n$ large enough such that
\[
c\max(L\lambda_n,  bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
\]
we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction.

@@

Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$.

For all $f \in \mathcal{C}^s[b,B,L]$,
\[
\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
\]
where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\

Step 1. We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.

\begin{align*}
|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 + w - f \|_n^2 - \| f_0 + w - f' \|_n^2| \\
	&\leq 2 \langle f_0 + w , f' - f \rangle_n + \| f \|_n^2 - \| f' \|_n^2\\
	&\leq 2 \| f_0 + w \|_n \| f' - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
\end{align*}

$\| f_0 + w \|_n \leq \| f_0 \|_n + \|w \|_n$. $\| w \|^2_n = \frac{1}{n}\sum_{i=1}^n w_i^2$ is the average of subexponential random variables. Therefore, for all $n$ larger than some absolute constant $n_0$, with probability at least $1-\frac{C}{n}$, $|\|w\|^2_n - \E|w|^2 | < \sigma^2 \sqrt{\frac{1}{cn} \log n}$. The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$.

$\|f_0\|^2_n$ is the average of random variables bounded by $B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E |f_0(X)|^2 | \leq B^2\sqrt{ \frac{1}{cn} \log n}$.

Since $\E|w|^2 \leq c\sigma^2$ and $\E| f_0(X)|^2 \leq B^2$, we have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 + w \|_n \leq c(B+\sigma)$.

@@

Thus, we have that, for all $n > n_0$,
\begin{align}
|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation1}
\end{align}
with probability at least $1-\frac{C}{n}$.

Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
\begin{align}
|R_s(f') - R_s(f)| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation2}
\end{align}

Lastly, we bound $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} \hat{R}_s(f') - R_s(f')$.

For a fixed $f'$, we have that, by definition
\[
\| f_0 + w - f' \|_n^2 = \| f_0 - f'\|_n^2 + 2 \langle w, f_0 - f'\rangle_n + \| w \|_n^2 \\
\]

Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $4(sB)^2$.

Using Hoeffding Inequality then, we know that the probability $| \| f_0 - f' \|_n^2 - \E(f_0(X) - f '(X))^2 | \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.

@@

Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
\[
C \exp( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} )
\]
for all $n > n_0$.

>>>>

Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)\big|^2 d \mathbf{x}_{-k}.
\]
It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.

@@

$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
\[
min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
                    \,:\, \E f_k(X_k) = 0 \}
\]
for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
\end{lemma}

@@

Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
\begin{align*}
 \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
\end{align*}

@@

For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0} - \bar{w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0} = \frac{1}{n} \sum_i f_0(X^{(i)})$ and $\bar{w} = \frac{1}{n}\sum_{i=1}^n w_i $ and $\mu = \E f_0(X)$. Note that we \emph{subtract} out the mean in the two risk definitions.

@@

\textbf{Note:} By definition of the Lipschitz condition, $f_k \in \mathcal{C}[b,B,L]$ implies that $\| \partial f_k \|_\infty \leq L$. $f = \sum_k f_k \in \mathcal{C}[s,b,B,L]$ implies that $\rho_n(f) \leq sL$.

@@

We first start with a lemma that converts assumption A4 into a more easily applicable condition.
\begin{lemma}
\label{lem:minus_one_risk_increase}
Suppose assumptions A1' and A4 hold.

@@

Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}[s,b,B,L], f_k \trm{ centered} \}$.

Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \rightarrow 0$.

Then, for all large enough $n$, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
\end{theorem}

@@

\textbf{Step 1:} $f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered. Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$.

\begin{align*}
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq 
               \| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w}\mathbf{1}_n 
                     - f^{*s} + \bar{f}^{*s}\mathbf{1}_n \|_n^2  - \| y - f^{*s}\|_n^2 \\
	&\leq 2\| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n -f^{*s}\|_n 
                \|\bar{f}^{*s} \mathbf{1}_n \|_n 
                  + \|\bar{f}^{*s} \mathbf{1}_n \|_n^2 \\
        &\leq 2 | \bar{f}^{*s} | \| f_0 + w 
           - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n - f^{*s} \|_n + |\bar{f}^{*s}|^2 
\end{align*}

Because each $f^{*s}$ is bounded by $sB$ and $\E f^{*s}(X) = 0$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}^{*s}| \leq sB \sqrt{\frac{1}{cn} \log n}$.

\begin{align*}
\| f_0 + w -\bar{f}_0\mathbf{1}_n 
                       - \bar{w} \mathbf{1}_n - f^{*s} \|_n 
	\leq \| f_0 - f^{*s} \|_n + \|w\|_n + |\bar{f}_0| + |\bar{w}|\\
\end{align*}

@@

$| \bar{f}_0 | \leq s B$ and $| \bar{w} | \leq c \sigma \sqrt{\frac{1}{n}}$ with probability at least $1-\frac{C}{n}$ by Chernoff bound.

So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
\[
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2c (sB+\sigma) sB \sqrt{\frac{1}{cn} \log n}
\]

\textbf{Step 2:} Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.

@@

Because we assume that we impose the Lipschitz constraint in our optimization, $\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $sL$ and so $|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2 sL \lambda_n$.

By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.

$\tau'_n$, as shown above, is at most $2 (sB+\sigma) sB \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.

For $n$ large enough such that
\[
c s L \lambda_n < \alpha \trm{ and } bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
\]
we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction since we assumed that $\hat{f}$ minimizes the regularized empirical risk.

@@

\begin{proof}
This proof uses a standard covering number argument.

Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$ such that for all $f \in \mathcal{C}[s,b,B,L]$, there exists $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ such that $\| f - f'\|_\infty \leq \epsilon$.

For all $f \in \mathcal{C}[s,b,B,L]$,
\[
\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
\]
where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\

\textbf{Step 1.} We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.

\begin{align*}
|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 - \bar{f}_0 + w - \bar{w} - f \|_n^2 
                                - \| f_0 - \bar{f}_0 + w -\bar{w} - f' \|_n^2| \\
	&\leq 2 \langle f_0 - \bar{f}_0 + w -\bar{w}, f' - f \rangle_n 
                            + \| f \|_n^2 - \| f' \|_n^2\\
	&\leq 2 \| f_0 - \bar{f}_0 + w -\bar{w} \|_n \| f' 
                   - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
\end{align*}

We now want to bound $\| f_0 - \bar{f}_0 + w -\bar{w} \|_n \leq \| f_0 \|_n  + \|w \|_n + |\bar{f}| + |\bar{w}|$.

$\| w \|^2_n = \frac{1}{n}\sum_{i=1}^n w_i^2$ is the average of subexponential random variables. Therefore, for all $n$ larger than some absolute constant $n_0$, with probability at least $1-\frac{C}{n}$, $|\|w\|^2_n - \E|w|^2 | < \sigma^2 \sqrt{\frac{1}{cn} \log n}$. The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$. Since $\E w^2 \leq \sigma^2$, for all $n > n_0$, with probability at least $1 - \frac{C}{n}$, for some constant $c$, $\| w \|^2_n \leq c \sigma^2$.

By Chernoff bound and the fact that $\E w = 0$, we know that $|\bar{w}| \leq c \sigma \sqrt{\frac{1}{n}}$ with high probability.

%$\|f_0\|^2_n$ is the average of random variables bounded by $s^2 B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E f_0(X)^2 | \leq s^2B^2\sqrt{ \frac{1}{cn} \log n}$. Since $\E f_0(X)^2 \leq s^2B^2$, we have that, for all $n > n_0$, with probability at least $1-\frac{C}{n}$, for some constant $c$, $\| f_0 \|_n^2 \leq c s^2 B^2$.

$\|f_0\|^2_n = \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})^2$. Since $f_0(X^{(i)})^2 \leq s^2 B^2$, $\|f_0\|^2_n \leq s^2 B^2$.

$|\bar{f}_0| = | \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})| \leq s B$.

Combining these together, We have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c ( s^2 B^2 +\sigma^2 )$, and so

\[
\|f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c (sB + \sigma)
\]

@@

Thus, we have that, for all $n > n_0$,
\begin{align}
|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon c( sB + \sigma ) \label{eqn:approx_deviation1}
\end{align}
with probability at least $1-\frac{C}{n}$.

\textbf{Step 2:} Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
\begin{align}
|R_s(f') - R_s(f)| \leq \epsilon c(sB + \sigma) \label{eqn:approx_deviation2}
\end{align}

\textbf{Step 3:} Lastly, we bound $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} \hat{R}_s(f') - R_s(f')$.

For a fixed $f'$, we have that, by definition
\begin{align*}
\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
     &= \| f_0  - \bar{f}_0\mathbf{1}_n - f'\|_n^2 
       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n - f'\rangle_n + \| w \|_n^2 + |\bar{w}|\\
R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
     &= \E\big(f_0(X) - \mu - f'(X)\big)^2 + \E w^2  
\end{align*}

Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.

Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.

@@

Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
\[
C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} \big)
\]
for all $n > n_0$.

### 2013-10-04 tex/scam/icml14/sparsistency_icml.tex
updated proof of additive faithfulness
proof and result update

\begin{packed_enum}
\item Let $F$ be a distribution supported and positive on $\mathcal{X}=[-b,b]^p$. Let $X^{(1)},..., X^{(n)} \sim F$ be iid.
\item Let $Y = f_0(X) + \epsilon$ where $\epsilon$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
\item Let $S = \{1,...,s\}$ denote the relevant variables where $s\leq p$, i.e.,
  $f_0(X) = f_0(X_S)$.
\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
\end{packed_enum}

Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
\item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
\item[A4:] For all $k=1,...,s$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
\end{packed_enum}

We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives. The $\alpha$ in assumption A4 can be interpreted as the signal strength of the relevant variable detection problem.

@@

@@

\begin{theorem} (Controlling false negatives)
\label{thm:false_negative}
Suppose assumptions A1', A2', A3 hold. Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint. Let $c,C$ be absolute constants.
Suppose $L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \right) \rightarrow 0$.
Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
\neq 0$ for all $k \in S$ with probability at least $1-\frac{C}{n}$.
\end{theorem}

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} and ignoring dependencies on $b,B,L,\sigma$,
we have the following result.
\begin{corollary}
  Assume A1', A2', A3. Let $\lambda_n = \Theta\left( \sqrt{
  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $\lambda_n
  \rightarrow 0$ and $\sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow
  0$. Let $\hat{f_n}$ be a solution to (\ref{opt:alternate_opt}) with
  boundedness and Lipschitz constraints. Then 
  $\P( \trm{supp}(\hat{f_n}) = \trm{supp}(f_0) ) \rightarrow 1$.
\end{corollary}
The above corollary implies that sparsistency is achievable at the same exponential scaling of the ambient dimension $p = O(\exp(n^c)), c<1$ rate as parametric models. The cost of nonparametric modeling is reflected in the scaling with respect to $s$, which can only scale at $o(n^{4/25})$.

@@

>>>>

\begin{packed_enum}
\item Let $F$ be a distribution supported and positive on $\mathcal{X}=[-b,b]^p$. Let $X^{(1)},..., X^{(n)} \sim F$ be iid.
\item Let $Y = f_0(X) + \epsilon$ where $\epsilon$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
\item Let $S = \{1,...,s\}$ denote the relevant variables where $s\leq p$, i.e.,
  $f_0(X) = f_0(X_S)$.
\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
\end{packed_enum}

Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
\item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq \E e^{\sigma^2 t^2 / 2}$.
\item[A4:] For all $k=1,...,s$, $\E(f^*_s(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
\end{packed_enum}

We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.

@@

\begin{remark}
Assumption A4 ensures that the relevant variables are ``relevant enough''. Under A4, the population risk of an additive function with $s-1$ components is at least $\alpha$ larger than the population risk of the optimal additive function with $s$ components. Lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
\end{remark}

@@

\begin{theorem} (Controlling false negatives)
\label{thm:false_negative}
Suppose assumptions A1', A2', A3, A4 hold. Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint. Let $c,C$ be absolute constants.
Suppose $s L \lambda_n \rightarrow 0$ and $bL (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow 0$.
Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
\neq 0$ for all $k \in S$ with probability at least $1-\frac{C}{n}$.
\end{theorem}

@@

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} and ignoring dependencies on $b,B,L,\sigma$,
we have the following result.
\begin{corollary}
  Assume A1', A2', A3, A4. Let $\lambda_n = \Theta\left( \sqrt{
  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $s \lambda_n
  \rightarrow 0$ and $\sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow
  0$. Let $\hat{f_n}$ be a solution to (\ref{opt:alternate_opt}) with
  boundedness and Lipschitz constraints. Then 
  $\P( \trm{supp}(\hat{f_n}) = \trm{supp}(f_0) ) \rightarrow 1$.
\end{corollary}
The above corollary implies that sparsistency is achievable at the same exponential scaling of the ambient dimension $p = O(\exp(n^c)), c<1$ rate as parametric models. The cost of nonparametric modeling is reflected in the scaling with respect to $s$, which can only scale at $o(n^{4/25})$.

@@

% DO NOT CHANGE; RefTex variables -minx

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "scam_icml.tex" ***
%%% End: ***
